Identifying covariate traits of trance and possession phenomena in the Ethnographic

### 2022-10-21 Readme.Rmd
whoopsie daisy

@@

ld = read_tsv('data/dat_long.tsv')
# wd = read_tsv('data/dat_wide.tsv')
sccs = filter(ld, in_sccs)
```

@@

| Relationship                                                                             | Reference                |
|:-----------------------------------|:-----------------------------------|
| less complexity $\rightarrow{}$ trance w/o possession                                    | @bourguignon1968         |
| women's social participation                                                             | @bourguignon1973religion |
| increased role differentiation and slavery parctices $\rightarrow$ trance and possession | @greenbaum1973           |
| main mode of subsistence                                                                 | @bourgouignon1977        |
| increased social participation $\rightarrow{}$ possession                                | @swanson1978             |
| more complexity $\rightarrow{}$ trance w/ possession                                     | @winkelman1986           |
| cognatic kinship $\rightarrow{}$ more possession and trance                              | @shaara1992              |
| decreased social participation $\rightarrow{}$ possession                                | @douglas2004natural      |
| monotheism                                                                               | @wood2018complexity      |

@@

The data are challenging in two ways. The variables are themselves correlated, either because they measure different facets of the same thing (like how complex a society is) or because they were adapted together by socially or geographically close societies (Galton's problem). In addition, data are missing from the Atlas in a non-random manner (e.g. if a society is hard to access, it is harder to provide a population size estimate for it).

>>>>

# To do: one-hot encoding ended up creating unidentifiable vars (where both values of a col are present) so do something with that.

@@

ld = read_tsv('data/dat_long.tsv')
wd = read_tsv('data/dat_wide.tsv')
sccs = filter(ld, in_sccs)
```

@@

| Relationship                                                                             | Reference                |
|:-----------------------------------|:-----------------------------------|
| Social complexity, rigidity, gender role differentiation                                    | @bourguignon1968         |
| Women's social participation                                                             | @bourguignon1973religion |
| Slavery, role differentiation, and structure differentiation | @greenbaum1973           |
| Increased social participation                                | @swanson1978             |
| Social complexity                                     | @winkelman1986           |
| Social flexibility, cognatic kinship                              | @shaara1992              |
| Decreased social participation                                | @douglas2004natural      |
| Social rigidity, monotheism                                                                               | @wood2018complexity      |

@@

The data are challenging in two ways. The variables are themselves correlated, either because they measure different facets of the same thing (like how complex a society is; see the figure below) or because they were adapted together by socially or geographically close societies (Galton's problem). In addition, data are missing from the Atlas in a non-random manner (e.g. if a society is hard to access, it is harder to provide a population size estimate for it).

```{r }
cord = wd %>% 
  filter(in_sccs) %>% 
  select(-outcome,-EA112_Trance_states,-trance_present,-possession_present,-possession_trance_present,-soc_id,-in_sccs) %>% 
  mutate_if(is.logical, as.double)

cor(cord,use="pairwise.complete.obs")
